Flatiron analysis

### 2021-04-02 Rmd/Report analysis 04022021.Rmd
Finished analysis html report

***
# Analysis Clinical

@@

## Clinical summary table
```{r analysis_data}
analysis_data <- Frontline %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

@@

## Plots for first treatment
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

@@

## Survivals by clinical

@@

***
# Analysis Treatment

## Treatment summary table

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## Survivals by treatment

@@

***
# RDI

## RDI summary table

@@

# Plots for first treatment
For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  group_by(treatment_sequence) %>% 
  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
  geom_bar(stat="identity")+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

@@

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
  geom_violin()+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
  theme_minimal()

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
  theme_minimal()+
  coord_flip()

@@

@@

## Survivals by RDI

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis Overall RDI", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of diagnosis carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of diagnosis cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of diagnosis all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of from first treatment overall RDI", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of from first treatment carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of from first treatment cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of from first treatment all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

***
# Hazard Ratio

@@

***
# Regression
## By clinical, demo
`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)`
```{r}
# Regression vital status prediction
model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

>>>>

***
# I.Analysis Clinical

@@

## 1.Clinical summary table
```{r analysis_data}
analysis_data <- Frontline %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

@@

## 3.Survivals by clinical

@@

***
# II.Analysis Treatment

## 1.Treatment summary table

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # group_by(treatment_sequence) %>% 
  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence,
             # y= percent, 
             fill = treatment_sequence))+
  geom_bar(
    # stat="identity"
    )+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

## 3.Survivals by treatment

@@

***
# III.RDI

## 1.RDI summary table

@@

## 2.Plots RDI
For RDI boxplot and violin, it is calculated for neoadjuvant and adjuvant when a patient got both (need to find another way of plotting to do by drug - maybe a wrap).

@@

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
  geom_violin()+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
  theme_minimal()

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
  theme_minimal()+
  coord_flip()

@@

```{r}
analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, alpha = mean_RDI_per_drug_chemotype<0.85))+
  geom_violin(aes(fill = drugname))+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
  theme_minimal()
```

@@

## 3.Survivals by RDI

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from diagnosis Overall RDI", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),

           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from diagnosis carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from diagnosis cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from diagnosis all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from first treatment overall RDI", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from from first treatment all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

## Survivals RDI by chemotherapy type
**On the left are Neoadjuvant, on the right are Adjuvant**

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp for platin
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by RDI_grp for taxel
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "taxel"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from from first treatment all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp for platin
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment carboplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from first treatment cisplatin", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by RDI_grp for taxel
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "taxel"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from from first treatment all taxel", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

***
# IV.Hazard Ratio

@@

***
# V.Regression
## By clinical, demo
`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)`
```{r}
# Regression vital status prediction
model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```
